Details matter: Similar host galaxies can harbor different merging compact binary populations

### 2016-07-11 paper/paper.tex
Updating

\begin{widetext}
% POINT:  Model
To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
\begin{eqnarray}
V(m_1,m_2) = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 d,m_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
\end{eqnarray}
where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
mergers, through the characteristic chirp mass $\mc_{C}\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron
stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum mass allowed by
\emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
  therein]{gwastro-EventPopsynPaper-2016}.  In agreement with much more detailed prior work \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, this simplified model yields typical chirp masses for BH-NS binaries that
vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume only comparable-mass binaries
form, with  component masses drawn from

@@

% POINT: 
To characterize how often compact binaries form and coalesce

% POINT: Simple model to encompass all
  Specifically, we encapsulate all information about
 binary evolution into two  parameterized response functions.  The function ${\cal G}(t| Z) =
dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,
given ambient metallicity $Z$.  The function $p(m_1,m_2|Z)$ is a metallicity-dependent mass distribution for binaries
formed in a metallicity $Z$.
%
Finally, we account for the substantially increased sensitivity of gravitational wave detectors to binaries of larger
chirp mass $\mc=(m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$; see \abbrvPSellipticals.
%
In terms of this response function, we can therefore calculate the relative contribution to the LIGO  event rate $r_D$
due to any individual galaxy via the following formula 
\begin{subequations}
\label{eq:RatePerGalaxy}
\begin{eqnarray}
r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  
 [\int d\mc p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}]
%\\
%% {\cal R}(z)&\equiv &  \int dx {\cal R} p(z)
\end{eqnarray}
\end{subequations}
In this expression, the galactic star formation rate
are galaxy-dependent and drawn from our
simulations.   \editremark{rewrite this to be average chirp mass at a given metallicity}

\end{widetext}
We parameterize the response function ${\cal G}(t|Z)$ with two factors: (a) an overall efficiency $\lambda$ for forming
binaries;  and (b) a
cumulative delay time distribution $P_t(<t|Z)$, describing the fraction of binaries born at $t=0$ that merge in less
than time $t$ from a population of binaries $Z$:\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
\begin{eqnarray}
G(t,x|Z) &=& \lambda(Z) p_x(x|Z) \frac{dP_t}{dt}(t) 
\end{eqnarray}
Previous studies suggest the number of merging compact binaries $\lambda \delta M_*$ produced by a starburst depends
as a power law on metallicity:
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{max}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).
In this paper we only investigate the dependence of rates with metallicity; we therefore  adopt 
\[
\lambda_0 = 10^{-3}/M_\odot
\]
as a typical value for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
%

For binaries containing neutron stars, for simplicity we adopt the universal delay time distribution
%% Finally, we parameterize the delay time distribution by  either
%% \begin{eqnarray}
%% P_t(<t) &=& \begin{cases}
%% 0 & t<10 \unit{Myr} \\
%% (t/13\unit{Gyr})^{b}& t \in [10\unit{Myr},t_H]
%% \end{cases} 
%% \end{eqnarray}
%% with $b> 0$ or as the special case
\begin{eqnarray}
\frac{dP_t(<t)}{dt} =  \begin{cases}
0 & t<10 \unit{Myr} \\
\frac{1}{t \ln (13 \unit{Gyr}/10\unit{Myr})} & t \in [10\unit{Myr},13\unit{Gyr}]
\end{cases} 
\end{eqnarray}
\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
  These variations have less impact on our results than the evolving metallicity distribution of star forming gas.}
%
For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
evolution  \citep{2010ApJ...715L.138B,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2-StarTrackRevised-2012}.

For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
and merger, as demonstrated in \abbrvPSellipticals{}.

Figure 2 of  \cite{2016arXiv160508783L} is an extreme example of this well-known trend

\editremark{Note}:

>>>>

\begin{widetext}
% POINT:  Model
To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
\begin{eqnarray}
V = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 dm_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
\end{eqnarray}
where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron
stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum
black hole mass $M_{max}(Z)$ allowed by
\emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
  therein]{gwastro-EventPopsynPaper-2016}.  In agreement with much more detailed prior work \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, this simplified model yields typical chirp masses for BH-NS binaries that
vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume  comparable-mass binaries
form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
 with $p=2$ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise; see, e.g.,
\cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
detection-weighted mass distribution [$\propto p(m_1,m_2)
\mc^{15/6}$] depends weakly on mass [$ p(m_1,m_2)
\mc^{15/6} \propto m_1^{-0.5} \delta(m_1-m_2)$.  In our simple model, the total  and chirp mass
distributions   are qualitatively consistent with detailed  binary evolution calculations \citep{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.

\end{widetext}

@@

% POINT: 
To characterize how often compact binaries form and coalesce, we use the ansatz adopted in \abbrvPSellipticals{} and
\abbrvPSgrb{}: for a star-forming parcel of mass $\Delta M$ the number of binaries born at time $0$ which
are coalescing now is $\lambda \Delta M dP/dt$, where $\lambda$ is an overall efficiency per unit mass and $P(<t|Z)$ is
a metallicity-dependent delay time distribution.\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
    In this paper we only investigate the relative contribution of
different star-forming environments, not the overall normalization, so the overall scale of $\lambda$ is irrelevant.  
However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact
objects, we adopt a power law
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{max}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adop a  concrete scale
factor  $
\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
%
For binaries containing neutron stars, for simplicity and without loss of generality we adopt the universal delay time distribution
%% Finally, we parameterize the delay time distribution by  either
%% \begin{eqnarray}
%% P_t(<t) &=& \begin{cases}
%% 0 & t<10 \unit{Myr} \\
%% (t/13\unit{Gyr})^{b}& t \in [10\unit{Myr},t_H]
%% \end{cases} 
%% \end{eqnarray}
%% with $b> 0$ or as the special case
\begin{eqnarray}
\frac{dP_t(<t)}{dt} =  \begin{cases}
0 & t<10 \unit{Myr} \\
\frac{1}{t \ln (13 \unit{Gyr}/10\unit{Myr})} & t \in [10\unit{Myr},13\unit{Gyr}]
\end{cases} 
\end{eqnarray}
\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
  These variations have less impact on our results than the evolving metallicity distribution of star forming gas.}
%
For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
evolution  \citep{2010ApJ...715L.138B,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2-StarTrackRevised-2012}.

For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
  an extreme example of this well-known trend.]  In practice, however, binary black holes produced near solar
metallicity correspond to a relatively small proportion of the overall population; we therefore neglect this
effect \footnote{may want to change}.
